---
title: "R Notebook"
output: html_notebook
---


measles.csv
variable	class	description
index	double	Index ID
state	character	School's state
year	character	School's district
name	character	School name
type	character	Whether a school is public, private, charter
city	character	City
county	character	County
district	logical	School district
enroll	double	Enrollment
mmr	double	School's Measles, Mumps, and Rubella (MMR) vaccination rate
overall	double	School's overall vaccination rate
xrel	logical	Percentage of students exempted from vaccination for religious reasons
xmed	double	Percentage of students exempted from vaccination for medical reasons
xper	double	Percentage of students exempted from vaccination for personal reasons

```{r}
#devtools::install_github("UrbanInstitute/urbnmapr")
#install.packages("ggridges")
extrafont::font_import()
extrafont::loadfonts()

```



```{r}
measles <- readr::read_csv('https://raw.githubusercontent.com/rfordatascience/tidytuesday/master/data/2020/2020-02-25/measles.csv',na = c('-1'))
tail(measles,20)
```



```{r}

library(tidyverse)
library(urbnmapr)
library(ggthemes)
library(cowplot)
library(ggridges)
library(santoku)

theme_update(
  plot.background = element_rect(fill = "black", color = "black"),
  panel.background = element_rect(fill = "black", color = "black"),
  panel.border = element_rect(fill = NA, color = NA),
  axis.line.x = element_line(color = "grey55", size = 1),
  axis.ticks = element_line(color = "grey55"),
  axis.title = element_text(color = "grey55", size = 12),
  axis.text = element_text(color = "grey55"),
  strip.background = element_rect(fill = NA, color = NA),
  legend.background = element_rect(fill = NA, color = NA),
  legend.key = element_rect(fill = NA, color = NA)
)
```

```{r}
states_sf <- get_urbn_map("states", sf = TRUE)
counties_sf <- get_urbn_map("counties", sf = TRUE)
colors <- c('#fe938c','#e6b89c','#ead2ac','#9cafb7','#4281a4')
```


,
         perc_xmed_chopped = chop(perc_xmed, breaks = c(0,5, 10, 20, 30 ,40), labels = c("Below 5%", "10%-20%", "20%-30%","30%-40%", "40%-50%"),drop = TRUE),

```{r warning=FALSE}


 measles_modified <- measles %>%
  #filter(!is.na(enroll)) %>%
  mutate(
    xmed = as.numeric(xmed),
    xper = as.numeric(xper),
    enroll = as.numeric(enroll),
    mmr = as.numeric(mmr),
    n_xmed = (xmed * enroll) / 100,
    n_xper = (xper * enroll) / 100
  )  %>%
   
  rename(state_name = state) 

county_mean <- measles_modified %>%
  group_by(state_name, county)  %>%
  
  summarize(
    mean_overal = mean(overall, na.rm = TRUE),
    mean_mmr = mean(mmr, na.rm = TRUE),
    is_xrel = if_else(max(xrel, na.rm = TRUE) == TRUE, TRUE, FALSE),
    sum_n_xmed = sum(n_xmed, na.rm = TRUE),
    sum_n_xper = sum(n_xper, na.rm = TRUE),
    perc_xmed = mean(xmed, na.rm = TRUE),
    perc_xper = mean(xper, na.rm = TRUE),
    
    
  ) %>%
  mutate(mean_mmr_chopped = chop(mean_mmr, breaks = c(0,30, 50, 70, 80 ,95,100), labels = c("0%-30%", "30%-50%", "50%-70%","70%-80%", "80%-95%","95%-100%")),
          perc_xper_chopped = chop( perc_xper, breaks = c(0,5, 10, 20, 30 ,40,50), labels = c("0%-30%", "10%-20%", "20%-30%","30%-40%", "40%-50%","Above 50%"),drop = TRUE),

         ) %>% 
  ungroup()

county_geo_merged <- counties_sf %>% 
  mutate(county = str_remove(county_name ,' County')) %>% 
    left_join(county_mean,by = c('state_name','county'))

state_mean <- measles_modified %>%
  group_by(state_name)  %>%
  summarize(
    mean_overal = mean(overall, na.rm = TRUE),
    mean_mmr = mean(mmr, na.rm = TRUE),
    is_xrel = if_else(max(xrel, na.rm = TRUE) == TRUE, TRUE, FALSE),
    sum_n_xmed = sum(n_xmed, na.rm = TRUE),
    sum_n_xper = sum(n_xper, na.rm = TRUE),
    perc_xmed = mean(xmed, na.rm = TRUE),
    perc_xper = mean(xper, na.rm = TRUE),
    
  ) %>%
  ungroup() %>% 
   mutate(mean_mmr_chopped = chop(mean_mmr, breaks = c(0,30, 50, 70, 80 ,95,100), labels = c("0%-30%", "30%-50%", "50%-70%","70%-80%", "80%-95%","95%-100%")))




```



```{r}
mmr_ridge_type_g <- measles_modified %>% 
filter(!is.na(type),type !='NA') %>% 
  #pivot_longer(c(mmr,xmed,xper),names_to = 'vac_status',values_to = 'rate') %>% 
ggplot(aes(x = mmr, y = type).fill = ) +
  geom_density_ridges(rel_min_height = 0.008,scale = 0.9) + 
  scale_x_continuous(breaks = c(0,20,40,60,80))  +
  scale_fill_distiller() +
  #facet_wrap(vac_status ~ .) +
  labs(x = 'Percentage', y = '') +
    theme_tufte()

xmed_ridge_type_g <- measles_modified %>% 
filter(!is.na(type),type !='NA') %>% 
ggplot(aes(x = xmed, y = type)) +
  geom_density_ridges(rel_min_height = 0.008,scale = 0.9) + 
  scale_x_continuous(breaks = c(0,20,40,60,80))  +
  scale_fill_distiller() + 
  labs(x = 'Percentage', y = '') +
    theme_tufte()

xper_ridge_type_g <- measles_modified %>% 
filter(!is.na(type),type !='NA') %>% 
ggplot(aes(x = xper, y = type)) +
  geom_density_ridges(rel_min_height = 0.008,scale = 0.9) + 
  scale_x_continuous(breaks = c(0,20,40,60,80))  +
  scale_fill_distiller() +
    theme_tufte()
```


```{r fig.height=8,fig.width=13}
"Fjalla One"
state_wide_map <- left_join(states_sf,state_mean,by = 'state_name')%>% 
  ggplot(aes(fill = mean_mmr,label = mean_mmr )) +
  geom_sf(color = "gray80") +
    geom_sf_text(aes(label = round(mean_mmr,0)),size = 4,family = 'Garamond') +
    scale_fill_continuous_tableau() +
    theme_void() +
  theme(legend.position = 'none',
        text = element_text(family = 'Garamond'))
 
state_wide_map    
```
```{r}

```


```{r}



counties_sf %>% 
  mutate(county = str_remove(county_name ,' County')) %>% 
    left_join(county_mean,by = c('state_name','county'))%>% 
  ggplot(aes(fill = mean_mmr,label = mean_mmr )) +
  geom_sf( color = "#ffffff") +
  labs(fill = 'MMR Rate',title = 'Measles, Mumps, and Rubella (MMR) vaccination rate') +
  scale_fill_gradientn(colors = colors) +
    theme_void() +
  theme(
    legend.position = 'top'
  )
  


mmr_county_map <- counties_sf %>% 
  mutate(county = str_remove(county_name ,' County')) %>% 
    left_join(county_mean,by = c('state_name','county'))%>% 
  ggplot(aes(fill = mean_mmr_chopped,label = mean_mmr )) +
  geom_sf( color = "#ffffff") +
  labs(fill = 'Vaccination Ratio:') +
  scale_fill_pander() +
    theme_void() +
  theme(legend.position = 'top')


mmr_county_map
```
```{r}

n_xmed_county_map <- county_geo_merged %>% 
  ggplot(aes(fill = sum_n_xmed,label = mean_mmr )) +
  geom_sf( color = "#ffffff") +
  scale_fill_gradientn(colors = colors) +
  #scale_fill_colorblind()
    theme_void()+
  theme(legend.position = 'top')
```

```{r}
 left_join(states_sf,state_mean,by = 'state_name')%>% 
  ggplot(aes(fill = sum_n_xmed )) +
  geom_sf( color = "#ffffff") +
  scale_fill_gradientn(colors = colors) +
  #scale_fill_colorblind()
    theme_void()+
  theme(legend.position = 'top')
ss```

```{r}
n_xper_county_map <- county_geo_merged %>% 
  ggplot(aes(fill = sum_n_xper,label = mean_mmr )) +
  geom_sf( color = "#ffffff") +
    #geom_sf_text(aes(label = round(mean_mmr,2))) +
    #scale_fill_continuous_tableau() +
  #scale_fill_gradient2_tableau() +
  scale_fill_gradientn(colors = colors) +
  #scale_fill_colorblind() + 
    theme_void() +
  theme(legend.position = 'top')
```



```{r fig.height=20,fig.width=15}
mmr_plots <-plot_grid(state_wide_map)
non_vac_plots <- plot_grid(mmr_county_map,n_xmed_county_map,n_xper_county_map,ncol = 3)

#ridge_type_plots <- plot_grid(mmr_ridge_type_g,xmed_ridge_type_g,xper_ridge_type_g,labels = 'auto',ncol = 3)
plot_grid(state_wide_map,non_vac_plots,facet_ridge,nrow = 3)
```


```{r, fig.height=20,fig.width=15}
mmr_grid <- plot_grid(mmr_county_map,mmr_ridge_type_g ,ncol = 2)
xmed_grid <- plot_grid(n_xmed_county_map,xmed_ridge_type_g ,ncol = 2)
xper_grid <- plot_grid(n_xper_county_map,xper_ridge_type_g ,ncol = 2)

#ridge_type_plots <- plot_grid(mmr_ridge_type_g,,,labels = 'auto',ncol = 3)
plot_grid(state_wide_map,mmr_grid,xmed_grid,xper_grid,nrow = 4)


"MMR Vacination Rate Accros counties"

'The left plot shows the average rate of vaccination for schools in each county'
'The left plot shows the number of students who were exempted from vacination due to medical reasons'

'The left plot shows the number of students who did not get vaccinated for personal reasons. On the right plot, we can see the distribution of the number of students who were exempted frfor different types of school'
'Number of Students Who Did Were Exempted from Vacination for Medical Reasons'


'Medical Reasons and Exemption from Vacination '

'Personal Reasons and Exemption from Vacination'
```




```{r}
facet_ridge <- measles_modified %>% 
filter(!is.na(type),type !='NA') %>% 
  pivot_longer(c(mmr,xmed,xper),names_to = 'vac_status',values_to = 'rate') %>% 
ggplot(aes(x = rate, y = type)) +
  geom_density_ridges(rel_min_height = 0.008,scale = 0.9) + 
  scale_x_continuous(breaks = c(0,20,40,60,80))  +
  #scale_fill_distiller() +
  facet_wrap(vac_status ~ .) +
    theme_tufte()
fact_ridge

```

